Online Tuning of EASY-Backfilling using Queue Reordering Policies.

### 2018-01-08 paper/src/paper.tex

Comparing algorithms in batch scheduling is made especially difficult by the
fluctuations in commonly used metrics~\cite{feitelson1998metrics}. The variability in
performance is known to outrank the available sample sizes: \textit{It is not
enough to simply replay an algorithm using a workload trace}. Indeed, as
presented in Figure~\ref{fig:variability}, the objective function we are using
in this work is subject to high variability. In our experience, randomly
shuffling months in a trace at random is enough to generate contradictory
conclusions about which algorithm is better. This is a known
problem~\cite{flurries} that motivated decades of research in workload
modeling~\cite{feitbook}. Workload models have drawbacks in that they usually
lose the details of the workloads. This is problematic due to the non-linear
aspect of the job scheduling process. This is discussed
in~\cite{feitresampling}, an approach which attempts to solve this problem by
resampling data directly from the original traces. In this work, we use a
simple implementation of these ideas. More precisely, we want to sample the job
submission process, which is achieved in the following manner: (a) For every
week in a resampled trace, we iterate over every existing user in the original
trace; (b) For each of these users, we choose a week of the original trace
uniformly at random; (c) The jobs from this user in this original week are
chosen to be present in the week being resampled. This simple mechanism enables
us to preserve the dependency within a week. Although the system state may not
be independent from one week to an other, we rely on existing
work~\cite{jsspp17} and assume for these experiments that the system is in a
stationary state. While we do provide guidelines as how to incorporate tracking
variant of our algorithms in Section~\ref{sec:online} by introducing a decaying
discount factor $\lambda$, this will not be studied in the experiments where
$\lambda=1$, and is left for future research.

>>>>

Comparing algorithms in batch scheduling is made especially difficult by the
fluctuations in commonly used metrics~\cite{feitelson1998metrics}. The variability in
performance is known to outrank the available sample sizes: \textit{It is not
enough to simply replay an algorithm using a workload trace}. Indeed, as
presented in Figure~\ref{fig:variability}, the objective function we are using
in this work is subject to high variability. In our experience, randomly
shuffling months in a trace at random is enough to generate contradictory
conclusions about which algorithm is better. This is a known
problem~\cite{flurries} that motivated decades of research in workload
modeling~\cite{feitbook}. Workload models have drawbacks in that they usually
lose the details of the workloads. This is problematic due to the non-linear
aspect of the job scheduling process. This is discussed
in~\cite{feitresampling}, an approach which attempts to solve this problem by
resampling data directly from the original traces. In this work, we use a
simple implementation of these ideas. More precisely, we want to sample the job
submission process, which is achieved in the following manner: (a) For every
week in a resampled trace, we iterate over every existing user in the original
trace; (b) For each of these users, we choose a week of the original trace
uniformly at random; (c) The jobs from this user in this original week are
chosen to be present in the week being resampled. This simple mechanism enables
us to preserve the dependency within a week. Although the system state may not
be independent from one week to an other, we rely on existing
work~\cite{jsspp17} and assume for these experiments that the system is in a
stationary state. We do provide guidelines as how to incorporate tracking
into our algorithms in Section~\ref{sec:online} by introducing a decaying
discount factor $\lambda$. Our experiments use stationary resampled data, 
and therefore no decay is necessary: $\lambda$ will be equal to $1$.
